On the characteristic and diameter of planar integral point sets \footnote{ The work of the first author was partially supported by the Theoretical Physics and Mathematics Advancement Foundation “BASIS”. }

### 2024-07-25 char-4k-bound/char-4k-bound.tex
[4k3] char385.png -> rails_2_14.png
[4k3] Fix duplicate ref

For convenience, we use the notation \cite{our-ped-2018,our-pmm-2018,our-vmmsh-2018}:
$\sqrt{p}/q * \{ (x_1,y_1), ...,$ $ (x_n, y_n)  \}$,
which means that each abscissa is multiplied by $1/q$
and each ordinate is multiplied by $\sqrt{p}/q$,  i.e.
\begin{equation}
	\label{eq:char_lattice}
	\sqrt{p}/q * \{ (x_1,y_1), ..., (x_n, y_n)  \}
	=
	\left\{ \left(\frac{x_1}{q},\frac{y_1\sqrt{p}}{q}\right), ..., \left(\frac{x_n}{q},   \frac{y_n\sqrt{p}}{q}\right)  \right\}
	,
\end{equation}
where $q$ is the characteristic of the IPS.
Such notation is made possible by the Grid Theorem.

@@

Figure~\ref{fig:char385} shows a rails IPS of characteristic $385 = 4 \cdot 96 + 1$ presented in~\cite{avdeev2019particular}.
Its coordinates are
\begin{multline}
	\sqrt{385}/{2} * \{ (\pm 1105, 48),
	(\pm 2189 ; 0),
	(\pm 1587 ; 0),
	(\pm 1269 ; 0),
	\\
	(\pm 763 ; 0),
	(\pm 623 ; 0),
	(\pm 529 ; 0),
	(\pm 339 ; 0)\}
\end{multline}

\begin{figure}
\center{\includegraphics[width=0.95\linewidth]{char385.png}}
\caption{IPS of cardinality 16 and diameter 2189}
\label{fig:char385}
\end{figure}

>>>>

For convenience, we use the notation \cite{our-ped-2018,our-pmm-2018,our-vmmsh-2018-translit}:
$\sqrt{p}/q * \{ (x_1,y_1), ...,$ $ (x_n, y_n)  \}$,
which means that each abscissa is multiplied by $1/q$
and each ordinate is multiplied by $\sqrt{p}/q$,  i.e.
\begin{equation}
	\label{eq:char_lattice}
	\sqrt{p}/q * \{ (x_1,y_1), ..., (x_n, y_n)  \}
	=
	\left\{ \left(\frac{x_1}{q},\frac{y_1\sqrt{p}}{q}\right), ..., \left(\frac{x_n}{q},   \frac{y_n\sqrt{p}}{q}\right)  \right\}
	,
\end{equation}
where $q$ is the characteristic of the IPS.
Such notation is made possible by the Grid Theorem.

@@

Figure~\ref{fig:rails_2_14} shows a rails IPS of characteristic $385 = 4 \cdot 96 + 1$ presented in~\cite{avdeev2019particular}.
Its coordinates are
\begin{multline}
	\sqrt{385}/{2} * \{ (\pm 1105, 48),
	(\pm 2189 ; 0),
	(\pm 1587 ; 0),
	(\pm 1269 ; 0),
	\\
	(\pm 763 ; 0),
	(\pm 623 ; 0),
	(\pm 529 ; 0),
	(\pm 339 ; 0)\}
\end{multline}

\begin{figure}
\center{\includegraphics[width=0.95\linewidth]{rails_2_14.png}}
\caption{IPS of cardinality 16 and diameter 2189}
\label{fig:rails_2_14}
\end{figure}
